QRF Covariate Selection

### 2020-09-21 analysis/R_scripts/fit_qrf_model.Rmd
edited code to deal with changes to snapPointsToLines output.
added code (but commented it out) for using fish / m2 as the response.

@@

# which of those sites are in Chinook domain?
chnk_sites = chnk_samps %>%
  as_Spatial() %>%
  maptools::snapPointsToLines(points = .,
                              lines = chnk_domain %>%
                                mutate(id = 1:n()) %>%
                                select(id, MPG) %>%
                                as_Spatial(),
                              maxDist = max_snap_dist,
                              withAttrs = TRUE,
                              idField = 'id') %>%
  as('sf') %>%
  select(-nearest_line_id, -snap_dist)

@@

# poss_hab_mets = c(poss_hab_mets, 'aug_temp', 'avg_aug_temp') %>%
#   unique()

@@

# filter out sites outside the Chinook domain
data("chnk_domain")
snap_dist = 1000

pred_hab_sites_chnk = pred_hab_sites %>%
  filter(!is.na(LON_DD)) %>%
  st_as_sf(coords = c('LON_DD', 'LAT_DD'),
           crs = 4326) %>%
  st_transform(crs = st_crs(chnk_domain)) %>%
  as_Spatial() %>%
  maptools::snapPointsToLines(chnk_domain %>%
                                mutate(id = 1:n()) %>%
                                select(id, MPG) %>%
                                as_Spatial(),
                              maxDist = snap_dist,
                              withAttrs = T,
                              idField = 'id') %>%
  as('sf') %>%
  as_tibble() %>%
  select(-nearest_line_id, -snap_dist, -geometry)

>>>>

# # to use fish / m2
# fish_hab %<>%
#   mutate(fish_dens = N / FishWettedArea) %>%
#   filter(!is.na(fish_dens),
#          FishWettedArea > 0)

@@

# which of those sites are in Chinook domain?
chnk_sites = chnk_samps %>%
  bind_cols(chnk_samps %>%
              as_Spatial() %>%
              maptools::snapPointsToLines(points = .,
                                          lines = chnk_domain %>%
                                            mutate(id = 1:n()) %>%
                                            select(id, MPG) %>%
                                            as_Spatial(),
                                          withAttrs = F,
                                          idField = 'id') %>%
              as('sf') %>%
              st_drop_geometry() %>%
              as_tibble() %>%
              select(snap_dist)) %>%
  filter(snap_dist <= max_snap_dist)

@@

@@

# # if using fish / m2 as response
# # predict at all CHaMP sites
# pred_hab_sites = hab_impute %>%
#   mutate(chnk_per_m2 = predict(qrf_mod,
#                               newdata = select(., one_of(covars)),
#                               what = pred_quant),
#          chnk_per_m2 = exp(chnk_per_m2) - dens_offset,
#          chnk_per_m = chnk_per_m2 * Area_Wet / Lgth_Wet)

# filter out sites outside the Chinook domain
data("chnk_domain")
my_snap_dist = 1000

pred_hab_sites_chnk = pred_hab_sites %>%
  filter(!is.na(LON_DD)) %>%
  bind_cols(pred_hab_sites %>%
              filter(!is.na(LON_DD)) %>%
              st_as_sf(coords = c('LON_DD', 'LAT_DD'),
                       crs = 4326) %>%
              st_transform(crs = st_crs(chnk_domain)) %>%
              as_Spatial() %>%
              maptools::snapPointsToLines(chnk_domain %>%
                                            mutate(id = 1:n()) %>%
                                            select(id, MPG) %>%
                                            as_Spatial(),
                                          idField = 'id') %>%
              as('sf') %>%
              as_tibble()) %>%
  filter(snap_dist <= my_snap_dist) %>%
  select(-nearest_line_id, -snap_dist, -geometry)
